How to Extract Maximum-Precision Radial Velocities from High-Resolution Spectra

### 2017-08-08 paper/paper.tex
more realistic fake spectra; template made by stacking epochs

for either of these, you could use:
\begin{itemize}
\item ``binary'' mask
\item synthetic spectrum
\item data-driven synthetic spectrum
\end{itemize}

@@

\section{Generating Test Spectra}

how the model works in general, Doppler shifting, parameterization of white noise. number of lines.

@@

another important consideration is how well the mask/template fits the data. summarize masks and templates tried (do they know the correct relative line depths and locations?).

\section{Single-Line Results}

\section{Multi-Line Results}

>>>>

for either of these, you could use:
\begin{itemize}
\item ``binary'' mask
\item synthetic spectrum (or template observation?)
\item data-driven template spectrum
\end{itemize}

@@

\section{Testing with Toy-Model Spectra}

The basic model that we use to generate fake spectra is extremely simple, assuming a perfectly normalized continuum; isolated, perfectly Gaussian spectral lines; and white noise only. We simulated a 5-$\AA$ region with random noise corresponding to an SNR of 100, a typical value for a single RV spectrum. Lines were inserted as Gaussians with arbitrarily-prescribed centers and depths (or equivalent widths). Every line was convolved with the same line spread function, which was taken to be a Gaussian with $\sigma$ = 0.05 $\AA$. %The number of lines used varies in the results discussed below.

We repeated this synthesis to make a set of 512 spectra, each with a random RV between -30 \kms and 30 \kms (the approximate amplitude of the yearly RV shifts induced by barycentric motion). The RVs can be applied as a straightforward Doppler shift in the centers of each line. \todo{(add equation?)} At this point, we are able to run a cross-correlation or a maximum-likelihood analysis on the set of spectra and examine the deviations in the recovered RVs from the input RVs.

\todo{remember to discuss quadratic max procedure.. probably in previous section?}

\subsection{Single-Line Results}

\subsection{Multi-Line Results}

\section{Dependence of RV Precision on Template Quality}

how well does the mask/template approximate the real data? try fudging the relative line depths and locations.

\section{Correlated Noise Sources and Their Consequences}

@@

\section{Application to Real Spectra}

how do our results compare to the reality of the situation? (will this tell us anything other than ``real spectra are more complicated and our template is silly''?)
